---
title             : "Week 5 Lab 8"
shorttitle        : "Wk5Lb8"

author: 
  - name          : "Shaina Trevino"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Maria Schweer-Collins"
    affiliation   : "1"
  - name          : "Alejandra Garcia Isaza"
    affiliation   : "1"
  - name          : "Jonathan Pedroza"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "University of Oregon"




abstract: |
  If You Have Two Loaves of Bread, Sell One and Buy a Lily - A Chinese Proverb
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Trains, Planes, Automobiles"


bibliography      : "refslab5.bib"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
library("rio")
library("dplyr")
library("here")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed,
                      echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5, 
                      fig.height = 8)
```

```{r load_data, include = FALSE}
d <- import(here("data", "star.csv"))
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis



# Results
The table below presents the mean scores and standard deviations for math and reading separated by sex(i.e., boys and girls) and whether these students receive free/reduced price meals or not.

``` {r table means sd, echo = FALSE}

sum_d <- d %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss),
            math_sd = sd(tmathss),
            rdg_mean = mean(treadss),
            rdg_sd = sd(treadss))

knitr::kable(sum_d, digits = 2)

```
# Discussion

Child maltreatment is characterized by its multifinality, this means that individual differences play a role in how child maltreatment is experienced and how it affects later development. In part, this can be explained by timing, dose, chronicity and type of maltreatment [@gunnar2006bringing]. For instance, Cowell, Cicchetti, Rogosch & Toth [-@cowell2015childhood] found that on measures of inhibitory control and working memory, maltreated children showed poorer performance than their non-maltreated counterparts. Furthermore, @cowell2015childhood found that within the maltreated group, children that had experienced maltreatment during infancy had worse performance in comparison with children that experienced maltreatment later in childhood. 



\newpage

# References






\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
